Temporal dataflow graphs and their application to generative music

### 2017-03-20 article-icmc2017.tex
save work

\documentclass[a4paper,twocolumns]{article}
\usepackage{microtype}
\usepackage{polyglossia}
\usepackage{geometry}
\setmainfont{Tribun ADF Std}

@@

\begin{document}
	\maketitle

@@

    The simplest strategy can be to only allow execution when all processes are active and have been given a definite order of execution : in this case the processes will only execute from $t=3$ to $t=5$ and behave like function composition. 
    While safe from the point of view of software execution, we will show that other execution policies leveraging information from the temporal layout of processes can provide composers with new creative capabilities.

    \subsection{Related works}
    Citer Kyma
    Céu
    Perl

    \subsection{Examples}
    Video filtering : 
    For t=0 to t=5 we change the brightness

    For t=3 to t=6 we change the contrast

@@

	\section{Graph definitions}
	\subsection{Why multiple graphs ?}
	\subsection{Hierarchy}

	\section{Inner data and outer data}
	Inner data : reduces the possibilities of connection : everything has to be there (explicit)

>>>>

\documentclass{article}

\usepackage{icmc2017template}
\usepackage{times}
\usepackage{ifpdf}
\usepackage{soul}
\usepackage{microtype}
\usepackage{polyglossia}
%\usepackage{geometry}

\def\papertitle{Paper Template for ICMC 2017}
\def\firstauthor{First Author}
\def\secondauthor{Second Author}
\def\thirdauthor{Third Author}
\def\fourthauthor{Fourth Author}
\def\fifthauthor{Fifth Author}
\def\sixthauthor{Sixth Author}

\threeauthors
{0.5in}
{\firstauthor} {Affiliation1 \\ %
    {\tt \href{mailto:author1@smcnetwork.org}{author1@smcnetwork.org}}}
{\secondauthor} {Affiliation2 \\ %
    {\tt \href{mailto:author2@smcnetwork.org}{author2@smcnetwork.org}}}
{\thirdauthor} { Affiliation3 \\ %
    {\tt \href{mailto:author3@smcnetwork.org}{author3@smcnetwork.org}}}

\usepackage[
pdftitle={\papertitle},
pdfauthor={\firstauthor, \secondauthor, \thirdauthor},
bookmarksnumbered, % use section numbers with bookmarks
pdfstartview=XYZ % start with zoom=100% instead of full screen; 
% especially useful if working with a big screen :-)
]{hyperref}
%\pdfcompresslevel=9

\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}

\usepackage[figure,table]{hypcap}

\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
}

@@

\begin{document}

    \capstartfalse
    \maketitle
    \capstarttrue

@@

    The simplest strategy can be to only allow execution when all processes are active and have been given a definite order of execution : in this case the processes will only execute from $t=3$ to $t=5$ and behave like function composition. 
    While safe from the point of view of software execution, we will show that other execution policies leveraging information from the temporal layout of the processes can provide composers with new creative capabilities.

    The main problem that arises is that composers may specify relationships between processes, but such processes may not always be active. 
    We start by making the case for an environment associated with the dataflow graph that contains the values of the inputs and outputs.
    Then, since a graph may not always be fully active, we show that it is also meaningful to have implicit connections between nodes of the graph, that will use the environment.
    This allows dynamic routing of the processes according to their temporal order during execution, and extends routing to pattern-matched elements of the environment instead of single values.
    We enumerate four different behaviours regarding the input and output parameters when the nodes are implicitely connected at runtime using the environment : strict, glutton, parallelized, and replaced. 
    Additionnaly, when the node are explicitely connected, we introduce a delay mechanism that allows a computation to happen on data previously produced by another node of the graph.
    \subsection{Related works}
    Citer Kyma
    Céu
    Perl

    \subsection{Examples}

@@

	\section{Graph definitions}
    We rely on two families of graphs for the execution of the software : 
    \begin{itemize}
        \item A dataflow graph between processes : processes have input and output ports that can be connected together to enforce data dependencies.
        \item A temporal graph, based on the OSSIA formalism: $G_t(V_t, E_t)$ where $V_t$ is the set of time nodes and $E_t$ is the set of time constraints in a score.
    \end{itemize}
    There may be more than a single temporal graph : they can be arranged hierarchically.

    The execution is driven by a scheduler.

    At each tick, the state of each temporal graph is updated with the following informations : 
    \begin{itemize}
        \item Which processes are currently running.
        \item For how long these processes have been running.
    \end{itemize}

    This is done according to the various events that occur and may trigger conditions and interaction points present in the temporal score.

    Event-driven vs time-driven vs sound-driven ; each node has a "driver" port which is the time or the sound. (Do like LV2 : pass empty buffers). Pb : multi-rate ... voir méthode pour passer de multi-rate à single rate dans PLOP2006 et Signal Flow Graphs and Data Flow Graphs (3.2, 3.3), dans Handbook of Signal Processing (First Edition)

    % Pour thèse : essayer de spécifier l'ensemble des cas possible / configuraitons d'activation de manière statique à partir d'un scénario donné, même si c'est exponentiel..

	%\subsection{Why multiple graphs ?}
	%\subsection{Hierarchy}

	\section{Implicit and explicit connections}
	Inner data : reduces the possibilities of connection : everything has to be there (explicit)
